---
title: "Alcohol vs Seat choice"
author: "David Santana"
date: "Fall 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

# introduction

$H_0$: There is no difference in the alcohol consumed based on the row you sit on.

$H_A$: There is a difference in the alcohol consumed based on the row you sit on.

# Method

the response variable is numerical and the explanatory variable is categorical.  therefore we use Numerical~cat.

## Results 

### Graphical Results 

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
this box plot shows the amount of alcohol consumed by the seating position.  The back seat consumes more than the front and middle seats.  the front and middle seats consume the same or very little difference.

  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The graph shows the amount of alcohol consumed based on where you sit. The back seat people consume more alcohol than the people who sit in the front and middle. the middle consumes more than the people who sit in the front. 

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

this data shows the mean and the median of alcohol consumed.  it also shows how they drink each quarter. the people in the back drink way more than the people in the front and middle.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
the p value is 0.000116 which is less than 0.5. the p value is smaller so therefore we reject the null hypothesis. this means that there is a difference in alcohol consumption based on where they sit.

```{r}
plot(TukeyHSD(model1))
```

we don't have evidence that there is a difference in the alcohol consumption between the middle and front rows. the only difference we found is the back row consumes more than the middle and front row.




# conclusion

is there a difference between the alcohol consumed between the row you choose to sit in? Yes there is a difference between the alcohol consumed by the row you sit in. based on the data the back row consumes more alcohol than the people who sit in the front and middle row. the p is 0.000116, which is smaller than 0.5, i will reject the null hypothesis.







